Inferring Graphics Programs from Images

### 2017-05-06 paper.tex
new figures and committed content you need to compile the paper

@@

\begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas] (canvas) at (0,-5) {};

@@

>>>>

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep network infer an execution trace from an image;
this recovers primitive drawing operations like lines, circles, or
arrows.  For added robustness we use the deep network as a proposal
distribution for a stochastic search over execution traces.
Finally we use techniques in the program synthesis community to
recover the program from its trace.

Each of these three components -- the deep network, the stochastic
search, the program synthesizer -- confers its own advantages. From
the deep network we get a very fast system that can recover plausible
execution traces in about a minute. From the stochastic search we get
added robustness; essentially the stochastic search can correct
mistakes made by the deep network's proposals.  From the program
synthesizer we get abstraction: our system recovers coordinate
transformations, for loops, and subroutines, which are useful for
downstream tasks.

@@

\begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas] (canvas) at (0,-5) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

@@

\section{Generalizing to hand drawings}

\begin{figure}
  \begin{minipage}[b]{0.3\textwidth}
    \centering\includegraphics[width = 3cm]{figures/expert-60.png}
    \subcaption{(a)}
  \end{minipage}%
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-groundTruth.png}
    \subcaption{(b)}
  \end{minipage}\\
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-1.png}
    \subcaption{(c)}
  \end{minipage}%
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-2.png}
    \subcaption{(d)}
  \end{minipage}
  \caption{(a): a hand drawing. (b): Rendering of the parse our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}
  \end{figure}
